### 2019-12-18 msr-paper/paper.tex
various corrections + acknowledgements

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Build failures are common in continuous integration (CI), but identifying the root cause of a failure is difficult.
Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
For each build log we manually labeled the log part (chunk) describing why the build failed.
We validated the data set by surveying the developers of the projects which produced the builds.
In addition, the data set categorizes the log chunks according to their format within the log text and provides keywords that a developer would use to search for the log chunks.
The width and depth of the \emph{LogChunks} data set makes it an ideal basis to further explore build log analysis, which can ultimately increase our understanding of CI build failures.
\emph{LogChunks} can be the basis to assess further build log analysis techniques and studies about why CI builds fail.

\end{abstract}

@@

\section{Introduction}
Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.

CI builds produce logs which report the results of the steps within the build.
These build logs contain a lot of valuable information for developers and researchers.
%Developers examine time measurement log statements to track how different stages of the build process perform.
%Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
Build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.

@@

These approaches have various strengths and weaknesses:
Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
Custom parsers are powerful though fragile towards changes in the log structure.
The structure of build logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
In addition, there is currently no data set available to evaluate and compare such chunk retrieval techniques for build logs.

@@

In this paper, we illustrate potential use cases of \emph{LogChunks}.% and our past study using the data set.
Section~\ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
The following section introduces the data schema, how to access the data set, as well as limitations and potential improvements.
We present our data collection in Section~\ref{sec:data-collection}.
To validate our labels we performed a second labeling of a sample of the data.
In addition, we surveyed the developers, whose commits triggered the builds, whether our labeled log chunk describes why their build failed.
Section~\ref{sec:validation} presents the two validation studies.
To conclude we describe limitations as well as potential improvements of \emph{LogChunks}.

@@

\begin{figure*}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXlX@{}}
  \toprule
  & Description & Unit & Example \\
  \midrule
  Log & relative path to the input build log & Path to Text File & Haskell/koalaman@shellcheck/failed/501296412.log \\
  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
  Keywords & keywords a developer would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
  \bottomrule
\end{tabularx}
\caption{Recommendations for each of the investigated chunk retrieval techniques}
\label{tab:single-technique-recommendations}
\end{figure*}

@@

\section{Conclusion}
In this paper, we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI\@.
For each log, we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
Still, there are limitations to our data set, which we present in the following.
We also propose several improvements and extensions to \emph{LogChunks}.
\label{sec:conclusion}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Build failures are common in continuous integration (CI), but identifying the root cause of a failure is difficult.
To stimulate research in this area, we present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
For each build log we manually labeled the log part (chunk) describing why the build failed.
We validated the data set by surveying the developers of the projects which produced the builds.
Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
Benchmarking different techniques will advance this research area and ultimately increase our understanding of CI build failures.
\end{abstract}

@@

\section{Introduction}
Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
CI builds produce logs which report the results of the steps within the build.
These build logs contain a lot of valuable information for developers and researchers.
%Developers examine time measurement log statements to track how different stages of the build process perform.
%Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

The problem is, that build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.

@@

These approaches have various strengths and weaknesses:
Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
Custom parsers are powerful though fragile towards changes in the log structure.
The structure of build logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
In addition, there is currently no data set available to benchmark such build log analysis techniques.

@@

% andy: okay if no structure overview in 4 page paper, place too valuable
% In this paper, we illustrate potential use cases of \emph{LogChunks}.% and our past study using the data set.
% Section~\ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
% The following section introduces the data schema, how to access the data set, as well as limitations and potential improvements.
% We present our data collection in Section~\ref{sec:data-collection}.
% To validate our labels we performed a second labeling of a sample of the data.
% In addition, we surveyed the developers, whose commits triggered the builds, whether our labeled log chunk describes why their build failed.
% Section~\ref{sec:validation} presents the two validation studies.
% To conclude we describe limitations as well as potential improvements of \emph{LogChunks}.

@@

\begin{figure*}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXlX@{}}
  \toprule
  & Description & Unit & Example \\
  \midrule
  Log & relative path to the input build log & Path to Log File & Haskell/koalaman@shellcheck/failed/501296412.log \\
  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
  Keywords & keywords a developer would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
  \bottomrule
\end{tabularx}
\caption{Recommendations for each of the investigated chunk retrieval techniques}
\label{tab:single-technique-recommendations}
\end{figure*}

@@

\section{Summary}
In this paper, we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI\@.
For each log, we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
Still, there are limitations to our data set, which we present in the following.
We also propose several improvements and extensions to \emph{LogChunks}.
\label{sec:conclusion}

### 2019-12-18 thesis/mini/abstract.tex
various corrections + acknowledgements

Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
This makes it hard to process and analyze them.
In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
We conduct an empirical study by comparing these techniques on our \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
Our findings show that none of the three techniques clearly outperforms the others.
We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.

>>>>

Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
This makes it hard to process and analyze them.
In this thesis, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
We conduct an empirical study by comparing these techniques on our \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
Our findings show that none of the three techniques clearly outperforms the others.
We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.

### 2019-12-18 thesis/mini/acknowledgments.tex
describe inter-rater reliability, conclusion and fw, add se logos
various corrections + acknowledgements

\vspace{1cm}
\noindent
%I want to thank Moritz Beller for: support when coming to delft, great support and detailed feedback. invaluable contribution to this work and the large amount of things I learned about reserach in these last five months
% annibale for his neverending input on study ideas, his expertise on information retrieval
% prof. pretschner for his feedback and critical questions on the whether my evaluation is actually meaningful
% prof. knapp?
% Taico for his relentless support, upcheering in the emotional valleys of throwing everything out of the window and listening to my enthusiastic detailed descriptions of ?
% Michi for his calming input and critical reflection of my working ethics
% my new founld colleagues from SERG (xavier, enrique, ayoushi, pouria, luis, joseph), sparking joy in lunch and coffee breaks, good breaks for my focussed mind
% the fourth floor group in welcoming me in a new country as I was one of them and showing me that even when you go to a completely new place you can find awesome friends there as well

>>>>

\vspace{1cm}
\noindent
I would like to thank Moritz for his great support, detailed feedback and his invaluable teaching how to do proper research.
I could not have imagined a better advisor for my master's thesis.

\noindent
Furthermore, I would like to thank Annibale for his helpful feedback and teaching me which is the proper vocabulary to describe my work.

\noindent
I want to pay my special regards to Prof. Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.

\noindent
I would like to acknowledge Martin, Martijn and Dominik for their thorough reviews.

\noindent
I am extremely grateful for my newfound friends, the fourth floor group and my colleagues from SERG.
Thank you for welcoming me with open arms and sparking joy in my days.

\noindent
Lastly, I want to thank Michi and Taico.
Thank you for your calming input, critical reflection, your relentless support and upcheering.

%I want to thank Moritz Beller for: support when coming to delft, great support and detailed feedback. invaluable contribution to this work and the large amount of things I learned about reserach in these last five months, aufbauendes feedback
% annibale for his neverending input on study ideas, his expertise on information retrieval, telling me the proper vocabulary to use and unlimited study and plotting ideas
% prof. pretschner for his feedback and critical questions on the whether my evaluation is actually meaningful and what problems I really solve
% prof. knapp? sharp eyes with formulas and /aufbauend/ words
% Michi for his calming input and critical reflection of my working ethics / balance.
% A big thank you to Martin, Taico, Martijn and Michi for their reviews.
% my new found colleagues from SERG (xavier, enrique, ayoushi, pouria, luis, joseph), sparking joy in lunch and coffee breaks and beer evenings
% the fourth floor group in welcoming me in a new country as I was one of them and showing me that even when you go to a completely new place you can find awesome friends there as well
% Lastly, Taico for his relentless support, upcheering in the emotional valleys of throwing everything out of the window and listening to my enthusiastic detailed descriptions of ?

### 2019-12-18 thesis/txt/0-introduction.tex
incorporate andys feedback v1
various corrections + acknowledgements

CI builds produce logs which report the progress and results of the steps within the build.
These build logs contain a lot of valuable information for developers and researchers.
Developers examine log statements of time measurements to track how different stages of the build process perform.
Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed tests to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

Build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.

>>>>

CI builds produce logs which report the results of the steps within the build.
These build logs contain a lot of valuable information for developers and researchers.
Developers examine log statements of time measurements to track how different stages of the build process perform.
Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed tests to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

The problem is, that build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.

### 2019-12-18 thesis/txt/3-data-set.tex
incorporate andys feedback v1
various corrections + acknowledgements

\section{Motivation}
We create \emph{LogChunks} as a data set for our empirical comparison study of the three chunk retrieval techniques PBE, CTS and KWS\@.
In the following, we motivate which repositories and build logs we collect and what data we label for each build log.

\paragraph{Log Collection}
Existing build log analysis approaches, like writing a custom parser and creating regular expressions, are specific to the build tools which create the targeted log output.
In contrast to that, our findings about the chunk retrieval techniques should not be specific to a specific build tool.
As the main development language in a repository influences the build tools, we want our comparison study and \emph{LogChunks} cover a wide array of development languages.
This is why we selected GitHub repositories from 29 different main development languages for our data set.

Examples configure the chunk retrieval techniques we investigate.
As the structure of a build log changes from project to project, these examples are specific to one project.
A user of a chunk retrieval technique has to manually create the examples for for each targeted information and project.
If the effort of creating examples should not too high, e.g. as high as developing a custom extraction program.
For that reason, we choose ten logs and examples per repository for \emph{LogChunks}.

@@

001- OK.
========DONE========
FAIL Bug #60120 (proc_open hangs when data in stdin/out/err is getting larger or equal to 2048) [ext/standard/tests/file/bug60120.phpt]</Chunk>
  </Example>
  ...
</Examples>
\end{lstlisting}

	\caption{Example XML file from \emph{LogChunks}}
	\label{lst:examples}
\end{figure}

@@

005-     Parameter #1 [ <optional> $ar_flags ]
========DONE========
FAIL Bug#71412 ArrayIterator reflection parameter info [ext/spl/tests/bug71412.phpt] 
*{\color{cyan}-=-=-=-=-=-}*
TEST 9895/13942 [2/2 concurrent test workers running]
\end{lstlisting}
	\caption{Log chunk with one line of context from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
	\label{lst:same-category}
\end{figure}

\begin{figure}[]
	\centering
\begin{lstlisting}[breaklines=true]
[0K$ ./sapi/cli/php run-tests.php -P -d extension=`pwd`/modules/zend_test.so $(if [ $ENABLE_DEBUG == 0 ]; then ...
*{\color{cyan}-=-=-=-=-=-}*
Illegal switch 'j' specified!
*{\color{cyan}-=-=-=-=-=-}*
Synopsis:
\end{lstlisting}
	\caption{Log chunk with one line of context from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
	\label{lst:different-category}
\end{figure}

>>>>

\section{Motivation}
We create \emph{LogChunks} as a data set for our empirical comparison study of the three chunk retrieval techniques PBE, CTS and KWS\@.
In the following, we motivate which repositories and build logs we collect and which data we label for each build log.

\paragraph{Log Collection}
Existing build log analysis approaches, like writing a custom parser and creating regular expressions, are specific to the build tools which create the targeted log output.
In contrast to that, our findings about the chunk retrieval techniques should not be specific to a particular build tool.
As the main development language in a repository influences the build tools, we want our comparison study and \emph{LogChunks} to cover a wide array of development languages.
This is why we selected GitHub repositories from 29 different main development languages for our data set.

Examples configure the chunk retrieval techniques we investigate.
As the structure of a build log changes from project to project, these examples are specific to one project.
A user of a chunk retrieval technique has to manually create the examples for for each targeted information and project.
The effort of creating these examples should not be too high, e.g. as high as developing a custom extraction program.
For that reason, we choose ten logs and examples per repository for \emph{LogChunks}.

@@

001- OK.
========DONE========
FAIL Bug #60120 (proc_open hangs when data in stdin/out/err is getting larger or equal to 2048) [ext/standard/tests/file/bug60120.phpt]</Chunk>
  </Example>
  ...
</Examples>
\end{lstlisting}
	\caption{Example XML file from \emph{LogChunks}}
	\label{lst:examples}
\end{figure}

@@

005-     Parameter #1 [ <optional> $ar_flags ]
========DONE========
FAIL Bug#71412 ArrayIterator reflection parameter info [ext/spl/tests/bug71412.phpt] 
*{\color{cyan}-=-=-=-=-=-}*
TEST 9895/13942 [2/2 concurrent test workers running]
\end{lstlisting}
	\caption[Log chunk from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}]{Log chunk from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from one line of context}
	\label{lst:same-category}
\end{figure}

\begin{figure}[]
	\centering
\begin{lstlisting}[breaklines=true]
[0K$ ./sapi/cli/php run-tests.php -P -d extension=`pwd`/modules/zend_test.so $(if [ $ENABLE_DEBUG == 0 ]; then ...
*{\color{cyan}-=-=-=-=-=-}*
Illegal switch 'j' specified!
*{\color{cyan}-=-=-=-=-=-}*
Synopsis:
\end{lstlisting}
	\caption[Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}]{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk one line of context}
	\label{lst:different-category}
\end{figure}

### 2019-12-18 thesis/txt/6-discussion.tex
various corrections + acknowledgements

\section{Recommendations of Suitable Techniques}
After discussing three chunk retrieval techniques separately we now want to unify out results into one recommendation scheme.
We present a decision tree, which asks questions to a developer or researcher who wants to retrieve information chunks from build logs.
The answers lead the user to more questions or the recommended technique as leaf nodes.
Figure~\ref{fig:crt-recommendation} presents the decision tree.

\emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
The recommendations are therefore likely based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
This decision tree is the answer to our first research question about which criteria influence the suitability of a chunk retrieval technique.
The earlier in the decision tree a criterion is noted, the more important it is when distinguishing the techniques.

@@

If the information chunks are from multiple structural categories, meaning the are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the precision or recall of the outcome and the user rather have output with low recall instead of no output at all.
When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.

@@

In our first example, a researcher studies whether there test failures in CI are caused by a small or by a large group of test cases.
They gather CI build logs from various projects, which are their only available data source.
The task of the researcher is to extract the name of the failing test case from each build log.
When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test case is in the investigated build logs.
As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, not predictable structural representations.
The next question is whether they value precision over recall.
As they have to manually inspect the results of both CTS and KWS, they choose recall over precision to avoid having to inspect the whole log in case the relevant information chunk was not retrieved.
Therefore, our decision tree recommends them to use KWS\@.

In case the researchers want to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each tes tool separately.

@@

\paragraph{Data Set}
The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
It only consists of build logs from open source and therefore it is not clear whether our results are generalizable to industry projects.
We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.

\paragraph{Training Set Size}
Especially the results for CTS might influenced by the fact that we only trained on one to five examples.
We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.

\paragraph{Few Samples with Many Structural Categories}
Our comparison study shows fewer measurements with many structural categories than with one category.
This stems from the fact that we use such a realistic data set which in many cases has only one or few structural categories.
% \bp{
% chronologically selected examples -> very specific view, devs/users might pick more representative examples

>>>>

\section{Recommendations of Suitable Techniques}
After discussing three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
We present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
The decision tree is built up of questions which either lead to more questions or to a leaf node containing a recommended technique.
Figure~\ref{fig:crt-recommendation} presents the decision tree.

\emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
The recommendations are therefore based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
This decision tree is the answer to our first research question about which criteria influence the suitability of a chunk retrieval technique.
The earlier in the decision tree a criterion is noted, the more important it is when distinguishing the techniques.

@@

If the information chunks are from multiple structural categories, meaning the are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the precision or recall of the outcome and the user would rather have output with low recall instead of no output at all.
When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.

@@

In our first example, a researcher studies whether test failures in CI are caused by a small or by a large group of test cases.
They gather CI build logs from various projects, which are their only available data source.
The task of the researcher is to extract the names of the failing test cases from each build log.
When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test cases is in the investigated build logs.
As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, not predictable structural representations.
The next question is whether they value precision over recall.
As they have to manually inspect the results of both CTS and KWS, they choose recall over precision to avoid having to inspect the whole log in case the relevant information chunk was not retrieved.
Therefore, our decision tree recommends them to use KWS\@.

In case the researchers want to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each test tool separately.

@@

\paragraph{Data Set}
The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
It only consists of build logs from open source projects and therefore it is not clear whether our results are generalizable to industry projects.
We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.

\paragraph{Training Set Size}
Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.

\paragraph{Few Samples with Many Structural Categories}
Our comparison study shows fewer measurements with many structural categories than with one category.
This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.
% \bp{
% chronologically selected examples -> very specific view, devs/users might pick more representative examples

### 2019-12-18 thesis/txt/7-conclusion.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text
various corrections + acknowledgements

\chapter{Conclusion and Future Work}
\label{sec:conclusion-fw}
The goal of this thesis is to support researches and developers when they decide how to analyze build logs.
We implemented and compared three different chunk retrieval techniques on our \emph{LogChunks} data set.
Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
Secondary factors are confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.

In the following we describe various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Further Analysis of the \emph{LogChunks} Data Set} We created the \emph{LogChunks} data set specifically for our comparison study, though it can be the basis for various further analyses of build log data.
  The keywords, for example, can be investigated to answer which keywords do developers use to search for the reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
  Our study design can be reused to evaluate other build log analysis techniques.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
  In a next step, each of these techniques could be refined and configured to better approach the domain of build logs.
  The \emph{LogChunks} data set and our study results act as a baseline to evaluate further technique improvements.
  We propose the following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
      We could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
      FlashExtract includes special tokens when enumerating possible regular expressions.
      We could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
      We propose to further investigate improvements in preprocessing of the log text, tokenization of the log lines into terms and stop words lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focussed on precision and recall.
  In addition to that, we propose to investigate how useful these outputs are to developers through controlled experiments.
\end{itemize}

>>>>

\chapter{Conclusion and Future Work}
\label{sec:conclusion-fw}
The goal of this thesis is to support researchers and developers when they decide how to analyze build logs.
We implemented and compared three different chunk retrieval techniques on our \emph{LogChunks} data set.
Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
Secondary factors are confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.

There are various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Further Analysis of the \emph{LogChunks} Data Set} We created the \emph{LogChunks} data set specifically for our comparison study, though it can be the basis for various further analyses of build log data.
  The keywords, for example, can be investigated to answer which keywords developers use to search for the reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
  Our study design can be reused to evaluate other build log analysis techniques.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
  In a next step, each of these techniques could be refined and configured to better approach the domain of build logs.
  The \emph{LogChunks} data set and our study results act as a baseline to evaluate further technique improvements.
  We propose the following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
      We could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
      FlashExtract includes special tokens when enumerating possible regular expressions.
      We could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
      We propose to further investigate improvements in preprocessing of the log text, tokenization of the log lines into terms and stop words lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
  In addition to precision and recall, we propose to investigate how useful these outputs are to developers through controlled experiments.
\end{itemize}
